\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - equations - 2 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Write each solution exactly. Show all of your work. You may use a calculator and notes. 
\begin{enumerate}
\newcommand{\spacing}{\vspace{0.50in}}

\item Voltage is given in terms of current and resistance by the formula $V=IR$. Solve the formula for the current $I$. 
	\spacing

\item The formula for simple interest is $I=Prt$. Solve this formula for the interest rate $r$. 
	\spacing

\item A formula says $P+Q=K$. Solve the formula for $Q$. 
	\spacing

\item Given $2t-3r=C$, solve for $t$. 
	\spacing

\item Given $\dfrac{a}{b}=\dfrac{x}{c}$, solve for $x$. 
	\spacing

\item Two boxes together weigh eighteen pounds. Write an equation describing this relationship in which $x$ and $y$ are the weights of the boxes. 
	\spacing

\item Two tanks together hold five thousand gallons. Write an equation describing this relationship in which $x$ and $y$ are the volumes of the tanks. 
	\spacing

\item Distance is equal to the product of rate and time. Write an equation describing this relationship, and solve that equation for the time $t$. 
	\spacing

\item A rope seventy-two feet long is cut into two pieces such that the second piece is eight feet longer than the first. How long is the shortest piece?
	\spacing

\item A rope sixty feet long is cut into two pieces such that the second piece is twice as long as the first. How long is the shortest piece?
	\spacing

\item A board ninety inches long is cut into three pieces such that the second is eighteen inches longer than the first, and the third is twice as long as the first. How long is each piece?
	\spacing

\item A cable one hundred twenty feet long is cut into three pieces such that the second it twelve feet longer than the first, and the third is two feet longer than the second. How long is each piece?
	\spacing

\item A rectangle is three feet longer than it is wide. Its perimeter is fifty-eight feet. Find the length and width of the rectangle.
	\spacing

\item A rectangle is twice as long as it is wide. Its perimeter is seventy-two feet. Find the length and width of the rectangle.
	\spacing

\item A rectangle is four times as long as it is wide. It's perimeter is sixty feet. Find the length and width of the rectangle.
	\spacing

\item A rectangle is seven feet longer than it is wide. It's perimeter is thirty-four feet. Find the length and width of the rectangle.
	\spacing

\end{enumerate}
\end{document}
