\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem Set - Decimals 1 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. 

For problems 1 through 4, round each decimal as indicated. 
\begin{multicols}{2}
\begin{enumerate}

    \item \hspace{0.250in} $12.435$; hundredth
  \vspace{0.25in}

    \item \hspace{0.250in} $0.0083$; thousandth
  \vspace{0.25in}

    \item \hspace{0.250in} $989.95$; tenth
  \vspace{0.25in}

    \item \hspace{0.250in} $2123.4$; hundred
  \vspace{0.25in}

\end{enumerate}
\end{multicols}
For problems 5 through 10, write each item as a decimal rounded to the nearest ten thousandth.
\begin{multicols}{2}
\begin{enumerate}
\setcounter{enumi}{4}

\item \hspace{0.25in} $\frac{5}{16}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $14\frac{2}{3}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $\frac{7}{8}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $5\frac{5}{12}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $\frac{52}{14}$ 
  \vspace{0.25in}
  
  \item \hspace{0.25in} $\frac{5}{9}$ 
  \vspace{0.25in}
  
\end{enumerate}
\end{multicols}
  \vspace{0.25in}
\begin{enumerate}
\setcounter{enumi}{10}
		\newcommand{\spacing}{\vspace{0.60in}}
\item What is the sum of $48.55$ and $12.78$? 
\spacing

\item Subtract $78.7$ from $210.12$.
\spacing

\item Multiply $1.81$ by $0.042$. 
\spacing

\item Write as a decimal the length forty-nine ten-thousandths of an inch. 
\spacing

\item Round to the nearest tenth the product of $12.2$ and $19.8$. 
\spacing

\item Round to the nearest tenth the ratio of $2.96$ feet to $1.25$ feet.  
\spacing

\item Find to the nearest hundredth $386.19$ divided by $12$.  
\spacing

\item If it takes $2.2$ cubic feet of acetylene to make one bracket, how many cubic feet are needed to make thirty brackets? 
\spacing

\item If a milling machine removes three thousandths of an inch per pass, how many passes are required to remove $0.024$ inches?
\spacing

\item A rod with a diameter of $\frac{7}{16}$ inches is turned on a lathe to a diameter of $0.375$ inches. To the nearest thousandth of an inch, by how much is the diameter of the rod reduced?
\spacing

\item If $3.2$ gallons of catalyst are required for every hundred gallons of solvent, how many gallons of catalyst are required for $250$ gallons of solvent? 
\spacing

\item Which is cheaper per foot, a $48$-foot piece of wire rope for \$17.89, or a $108$-foot piece for \$37.79? 

\end{enumerate}
\end{document}
