\documentclass[12pt,fleqn]{article} %left-align equations
\usepackage{amssymb,amsmath,latexsym,mdwlist,multicol,enumitem,gensymb}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
		\newcommand{\spacing}{\vspace{0.80in}}
\begin{center}
          Problem set - feet and inches - 2 \\[0.5in]
\end{center}
  \vspace{0.25in}

Name: \rule{4in}{0.005in} Date: \rule{1.4in}{0.005in} 

\begin{enumerate}

  \item A measurement is 3 feet 8 inches. How many inches is this? 
  \spacing

  \item A measurement is 4 yards 2 feet 9 inches. How many inches is this? 
  \spacing

  \item Write 62$''$ in feet and inches. 
  \spacing

  \item A part is to be 7$''$ wide. To the nearest tenth of a foot, what is this dimension in decimal feet? 
  \spacing

  \item A part is to be 2$'$ 9$''$ long. What is this dimension in decimal feet? 
  \spacing

  \item A piece of material 8$'$ 9$''$ long is to be cut into 5 equal pieces. How long will each piece be, ignoring the width of the cut?
  \spacing

  \item Write in decimal feet to the nearest hundredth of a foot 4$'$ 5$\frac{3}{8}$ inches. 
  \spacing

  \item Write in decimal feet to the nearest hundredth of a foot 2$'$ 10$\frac{1}{4}$ inches. 
  \spacing

  \item Write in decimal feet to the nearest hundredth of a foot 1$'$ 3$\frac{3}{16}$ inches. 
  \spacing

  \item Write in inches to the nearest quarter inch 3.746 feet. 
  \spacing

  \item Write in feet and inches to the nearest eighth of an inch 6.368 feet. 
  \spacing

  \item Write in feet and inches to the nearest eighth of an inch 42.79 inches. 
  \spacing

  \item Twelve pieces are to be cut from half-inch bar stock. Each of the Twelve is to be 1$'$ 4$\frac{3}{4}$ inches long. Ignoring the width of the cut, write in feet and inches rounded up to the nearest inch the minimum length of bar stock required. 
  \spacing

  \item A strip of aluminum 14$'$ 2$''$ long is to be cut into ten equal pieces. What is the length of each piece in feet and inches? 
  \spacing

\end{enumerate}
\end{document}
