\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - rates \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. 

\begin{enumerate}
		\newcommand{\spacing}{\vspace{0.70in}}

\item A commodity costs \$4.50 per ton. 
	\begin{enumerate}
		\item How much will forty-eight tons cost? 
\spacing

		\item How many tons can you get for \$1,800? 
\spacing
	\end{enumerate}

\item A shark swims at eight miles per hour.  
	\begin{enumerate}
		\item How long does it take to swim thirty-six miles? 
\spacing

		\item How far can it swim in $4.5$ hours? 
\spacing
	\end{enumerate}

\item A fan moves $675$ cubic feet of air per minute.   
	\begin{enumerate}
		\item How long does it take to move $5219$ cubic feet?  
\spacing

		\item How many cubic feet does it move in eight hours? 
\spacing
	\end{enumerate}

\pagebreak
		 
\item Thirty tons of aggregate costs \$120.   
	\begin{enumerate}
		\item How much does aggregate cost per ton?
\spacing

		\item To the nearest ton, how much can you buy for \$750?
\spacing
	\end{enumerate}

\item A train travels $945$ miles in $21$ hours. 
	\begin{enumerate}
		\item What is its average speed? 
\spacing

		\item How far can it travel in $15$ hours? 
\spacing
	\end{enumerate}

\item A pump moves $14$ gallons of water in 2.1 hours.   
	\begin{enumerate}
		\item To the nearest tenth, what is its delivery rate in gallons per hour?  
\spacing

		\item How long does it take to move eight hundred gallons? 
\spacing
	\end{enumerate}

\item At an average speed of $52$ miles per hour, 
	\begin{enumerate}
		\item how far can you go in six hours?  
\spacing

		\item how long does it take to go 500 miles, to the nearest tenth of an hour? 
\spacing
	\end{enumerate}

\end{enumerate}
\end{document}
