\documentclass[12pt,fleqn]{article} %left-align equations
\usepackage{amssymb,amsmath,latexsym,mdwlist,multicol,enumitem,gensymb}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
		\newcommand{\spacing}{\vspace{0.70in}}
\begin{center}
          Problem set - Time - 2 \\[0.5in]
\end{center}
  \vspace{0.25in}

Name: \rule{4in}{0.005in} Date: \rule{1.4in}{0.005in} 

\begin{enumerate}

  \item How many hours is 300 minutes? 
  \spacing

  \item How many minutes is 1$\frac{1}{5}$ hours? 
  \spacing

  \item How many hours and minutes is 221 minutes? 
  \spacing

  \item In hours and minutes to the nearest minute how long is 5.2 hours? 
  \spacing

  \item In hours and minutes the nearest minute how long is 2.43 hours? 
  \spacing

  \item Write in hours and minutes the sum of 2 hours 18 minutes, 3 hours 6 minutes, and 1 hour 36 minutes.
  \spacing

  \item Subtract 2 hour 52 minutes from 4 hours.
  \spacing

  \item Write in degrees and minutes to the nearest minute the angle 50.9\degree. 
  \spacing

  \item Write in degrees and minutes to the nearest minute the angle 121.42\degree. 
  \spacing

  \item Write in decimal degrees to the nearest hundredth of a degree 18\degree 24$'$ 34$''$. 
  \spacing

  \item Write in decimal degrees to the nearest hundredth of a degree 64\degree 12$'$ 46$''$. 
  \spacing

  \item What is the complement of an angle measuring 58\degree\ 20$'$ 25$''$?
  \spacing

  \item What is the complement of an angle measuring 35\degree\ 16$'$ 48$''$?
  \spacing

  \item What is the supplement of an angle measuring 120\degree\ 26$'$ 8$''$?
  \spacing

  \item One angle in a right triangle measures 33\degree\ 28$'$ 2$''$. What is the measure of the other angle? 
  \spacing

  \item One angle in a right triangle measures 54\degree\ 10$'$ 36$''$. What is the measure of the other angle? 
  \spacing

\end{enumerate}
\end{document}
