\documentclass[12pt,fleqn]{article} %left-align equations
\usepackage{amssymb,amsmath,latexsym,mdwlist,multicol,enumitem,gensymb}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
		\newcommand{\spacing}{\vspace{0.70in}}
\begin{center}
          Problem set - Time - 1 \\[0.5in]
\end{center}
  \vspace{0.25in}

Name: \rule{4in}{0.005in} Date: \rule{1.4in}{0.005in} 

\begin{enumerate}

  \item How many minutes is 2.5 hours? 
  \spacing

  \item How many minutes is 3$\frac{2}{5}$ hours? 
  \spacing

  \item How many hours and minutes is 148 minutes? 
  \spacing

  \item In hours and minutes to the nearest minute how long is 2.77 hours? 
  \spacing

  \item In hours and minutes the nearest minute how long is 1.84 hours? 
  \spacing

  \item Add up 1 hour 20 minutes, 2 hours 48 minutes, and 1 hour 16 minutes.
  \spacing

  \item Subtract 1 hour 48 minutes from 3 hours 30 minutes.
  \spacing

  \item Write in degrees and minutes to the nearest minute the angle 42.29\degree. 
  \spacing

  \item Write in degrees and minutes to the nearest minute the angle 91.94\degree. 
  \spacing

  \item Write in decimal degrees to the nearest hundredth of a degree 12\degree 22$'$ 38$''$. 
  \spacing

  \item Write in decimal degrees to the nearest hundredth of a degree 88\degree 4$'$ 52$''$. 
  \spacing

  \item What is the complement of an angle measuring 68\degree\ 18$'$ 24$''$?
  \spacing

  \item What is the complement of an angle measuring 21\degree\ 5$'$ 42$''$?
  \spacing

  \item What is the supplement of an angle measuring 110\degree\ 24$'$ 52$''$?
  \spacing

  \item One angle in a right triangle measures 22\degree\ 28$'$ 2$''$. What is the measure of the other angle? 
  \spacing

  \item One angle in a right triangle measures 40\degree\ 4$'$ 20$''$. What is the measure of the other angle? 
  \spacing

\end{enumerate}
\end{document}
