\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}
\usepackage{pgf}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem Set - Proportions 2\\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. You may use a calculator and notes. 

\begin{enumerate}

\item If 8 items cost \$24, what will 110 items cost, at the same rate? 
  \vspace{0.5in}

\item If 2 barrels of flour cost \$15, what will 12 barrels cost? 
  \vspace{0.5in}

\item If a car gets 26 miles per gallon, how far to the nearest mile can it go on 20 gallons? 
  \vspace{0.5in}

\item If I walk 168 miles in 6 days, how far can I walk, at the same rate, in 18 days? 
  \vspace{0.5in}

\item If 8 lb. of sugar cost \$1.28, how much will 13 lb. cost? 
  \vspace{0.5in}

\item If 300 barrels of flour cost \$2100, what will 125 barrels cost? 
  \vspace{0.5in}

\item If 120 sheep yield 330 pounds of wool, how many pounds will 36 sheep yield? 
  \vspace{0.5in}

\item If 80 yards of cloth cost \$340, what will 650 yards cost? 
  \vspace{0.5in}

\item Use a proportion to find the value of four hundred pounds of sugar at five cents per pound.  
  \vspace{0.5in}

\item If a dog can complete a journey in 8 days, walking 9 hours a day, how many days will it require if the dog walks 10 hours a day? 
  \vspace{0.5in}

\item If 16 lions consume 560 pounds of meat in a month how much will 40 lions consume in a month? 
  \vspace{0.5in}

\item A certain amount of food will feed 900 pandas for 90 days: if the number of pandas is increased by 600, now long will the same amount of food feed them? 
  \vspace{0.5in}

\item What will 26.25 bushels of wheat cost, if 3.5 bushels cost \$8.40? 
  \vspace{0.5in}

\item If $\frac{1}{2}$ of an ounce costs \$0.90, what will $1\frac{1}{2}$oz. cost? 
  \vspace{0.5in}

\item If one barrel of solvent is enough for 1250 parts, how many barrels are enough for 10,000 parts? 
  \vspace{0.5in}

\item If 90 sacks of feed will satisfy 100 marmots for 120 days, how long will 90 sacks satisfy 75 marmots? 
  \vspace{0.5in}

\item If a staff, 5 feet long, casts a shadow of 7 feet, what is the height of a steeple, whose shadow is 196 feet, at the same time of day? 
  \vspace{0.5in}

\item A certain job can be done in 12 days, by working 4 hours each day: how many days would it require to do the same job, by working 9 hours a day? 
  \vspace{0.5in}
 
\end{enumerate}
\end{document}
