\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - Dimensional analysis - 2 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Use dimensional analysis to answer the questions. Show all of your work. You may use a calculator and notes. 

There are 12 inches in one foot, 3 feet in one yard, and 1760 yards in one mile. One meter is 39.37 inches. 

\newcommand{\spacing}{\vspace{0.80in}}
\begin{enumerate}
\item How many inches is 23 feet? 
\spacing

\item How many inches is $4\frac{2}{3}$ yards? 
\spacing

\item How many feet is 0.25 miles? 
\spacing

\item How many yards is 162 inches? 
\spacing

\item To the nearest hundredth of a meter, how many meters is 16 inches? 
\spacing

\item To the nearest meter, how far is 6.2 miles? 
\spacing

		\suspend{enumerate}
There are sixteen ounces in one pound, and two thousand pounds in one ton. A kilogram is 2.205 pounds. 
		\resume{enumerate}

\item How many pounds is $1\frac{5}{8}$ ton? 
\spacing

\item How many tons is $6,000$ pounds? 
\spacing

\item How many ounces is half a kilogram?  
\spacing

		\suspend{enumerate}
There are eight fluid ounces in a cup, two cups in a pint, two pints in a quart, and four quarts in a gallon. One liter is 33.81 fluid ounces. 
		\resume{enumerate}

\item How many ounces is half a cup? 
\spacing

\item How many gallons is forty-eight pints?  
\spacing

\item How many quarts is 128 ounces? 
\spacing

\item To the nearest tenth of a liter, how many liters is 10 gallons? 
\spacing

\end{enumerate}
\end{document}
