\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - Dimensional analysis \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Use dimensional analysis to answer the questions. Show all of your work. You may use a calculator and notes. 

There are 12 inches in one foot, 3 feet in one yard, and 1760 yards in one mile. One meter is 39.37 inches. 

\newcommand{\spacing}{\vspace{0.80in}}
\begin{enumerate}
\item How many inches is 16.5 feet? 
\spacing

\item How many inches is 2.5 yards? 
\spacing

\item How many feet is 1.4 miles? 
\spacing

\item How many yards is 216 inches? 
\spacing

\item To the nearest hundredth of a meter, how many meters is 408 inches? 
\spacing

\item To the nearest meter, how far is 3.1 miles? 
\spacing

		\suspend{enumerate}
There are sixteen ounces in one pound, and two thousand pounds in one ton. A kilogram is 2.205 pounds. 
		\resume{enumerate}

\item How many pounds is $\frac{1}{4}$ ton? 
\spacing

\item How many tons is $8,000$ pounds? 
\spacing

\item How many ounces is two kilograms?  
\spacing

		\suspend{enumerate}
There are eight fluid ounces in a cup, two cups in a pint, two pints in a quart, and four quarts in a gallon. One liter is 33.81 fluid ounces. 
		\resume{enumerate}

\item How many ounces is three cups? 
\spacing

\item How many pints is one gallon?  
\spacing

\item How many quarts is 256 ounces? 
\spacing

\item How many liters is 16 gallons? 
\spacing

\end{enumerate}
\end{document}
