\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - percents - 3 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Unless directed otherwise, round answers to the nearest hundredth, or to the nearest percent. Show all of your work. You may use a calculator and notes. 
\begin{enumerate}
\item Write $\frac{19}{32}$ as a percent rounded to the nearest tenth of a percent. 
	\vspace{0.260in}

\item Write $1\frac{1}{5}$ as a percent rounded to the nearest tenth of a percent. 
	\vspace{0.260in}

\item Write $0.0035$ as a percent.
	\vspace{0.260in}

\item Write $0.8\%$ as a fraction in lowest terms.
	\vspace{0.260in}

\item Write $88.56\%$ as a fraction in lowest terms.
	\vspace{0.260in}

\item On a particular job materials cost \$75 and labor costs \$96. To the nearest whole percent, what fraction of the total is labor?
	\vspace{0.280in}

\item Forty percent of a particular job is labor. If the job costs \$1,200 how much does the labor cost?
	\vspace{0.280in}

\item Pat gets a commission on sales of 0.5\%. If Pat sells \$68,000 worth of parts, what is Pat's commission? 
	\vspace{0.280in}

\item Carl gets a commission on sales of 2.5\%. How much does Carl need to sell to get a commission of \$900?
	\vspace{0.280in}

\pagebreak

\item A series of dimensions are to be within $\pm5\%$. What is the maximum and minimum acceptable dimension in each case? 
    \begin{enumerate}
	\item 7.55 inches
  \vspace{0.250in}
	\item 28.0 inches
  \vspace{0.250in}
	\item 72.5 inches
  \vspace{0.250in}
	\item 143 inches
  \vspace{0.250in}
    \end{enumerate}
  \vspace{0.250in}

\item A part is to be 1.2 inches in diameter, $\pm5\%$. It measures 1.27 inches. Is this acceptable? 
  \vspace{0.50in}

%\item If gasoline increased from \$3.50 per gallon to \$3.75 per gallon, by what percent did the price increase? 
%  \vspace{0.50in}
%
%\item If gasoline decreased from \$3.75 per gallon to \$3.50 per gallon, by what percent did the price decrease? 
%  \vspace{0.50in}

%\item If the production per shift decreased from eight thousand units to seven thousand five hundred units, by what percent did the production rate decrease? 
%  \vspace{0.50in}
%
% moved percent change to tech math for su19
\item Solvent, regularly \$18.59 per gallon, is on sale for 20\% off. What is the sale price?
  \vspace{0.50in}

\item Apex bought a machine for \$180,000, borrowing \$170,000 and paying the rest in cash. What percent of the purchase price did Apex pay in cash?
  \vspace{0.50in}

\item Out of a production run of three hundred thousand, 31 parts were rejected as too large, and 24 as too small. What percent of the run was rejected? 
  \vspace{0.50in}

\item If $0.02\%$ of parts may be out of spec, would 48 out-of-spec parts be acceptable in a production run of 220,000? 
  \vspace{0.50in}

%\item After a price reduction of 20\%, an injection molding feeder unit sells for \$17,000. What was the price before the reduction? 
%  \vspace{0.50in}
%
  \item In January a bridge span is at its minimum length of 999.65 meters. In August, because of thermal expansion, it measures 1000.45 meters, its maximum length. Throughout that period, is the bridge span 1000m $\pm0.1\%$ long?
  \vspace{0.50in}

%  \item The components of a mixture are in a ratio of 247:171:20. To the nearest hundredth of a percent, what percent of the mixture is each component?
%  \vspace{0.50in}
%
%  \item A particular bronze alloy is 8\% tin, 0.25\% phosphorus, and the rest copper. 
%      \begin{enumerate}
%	  \item How much of each component is required for 1,000 pounds of alloy?
%	      \vspace{0.5in}
%	  \item What is the ratio of copper to tin to phosphorus in lowest terms? 
%	      \vspace{0.5in}
%       \end{enumerate}
%
\end{enumerate}
\end{document}
