\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - whole numbers - 2 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Show all of your work. You may use a calculator to check your answer. 

\begin{enumerate}

\item At the beginning of the first shift, Tegula International had an inventory of $64,000$ roof tiles. During the shift, they manufactured $120,000$ tiles, and shipped out $144,000$ tiles to fulfill an order from a customer. How many tiles were left in inventory at the end of the first shift?  
  \vspace{0.5in}
  \vspace{0.5in}

\item A bundle of odd lengths of aluminum channel contains five pieces that are 4' long, three pieces that are 5' long, and one piece that is 6' long. How many linear feet of channel are in the bundle?
  \vspace{0.5in}
  \vspace{0.5in}

\item Acme sold one hundred fifty-three wiring sub-assemblies, and made a total profit of seven thousand four hundred ninety-two dollars. To the nearest cent, what was Acme's profit on each sub-assembly?
  \vspace{0.5in}
  \vspace{0.5in}
  \vspace{0.5in}

\item From a new 50-foot roll of wire a man cut pieces 8', 14', 3', and 5' long. How much wire should be left on the roll? 
  \vspace{0.5in}
  \vspace{0.5in}

\item A bill of material requires forty-eight pieces of bar stock, each piece eight inches long. How many feet of bar stock does the bill of material require? 
  \vspace{0.5in}
  \vspace{0.5in}

\item If a manufacturing cell produces 92 assemblies per hour, how many will it produce in 16 hours? 
  \vspace{0.5in}
  \vspace{0.5in}

\item A water tank holds 2800 gallons. If 400 gallons per day are used, how many days will the tank last? 
  \vspace{0.5in}
  \vspace{0.5in}

\item Louisa's delivery truck gets twelve miles per gallon. If fuel costs three dollars per gallon, how much will it cost in fuel to make deliveries of $8$ miles, $12$ miles, $5$ miles, $2$ miles, $19$ miles, and $14$ miles? 
  \vspace{0.5in}
  \vspace{0.5in}
  \vspace{0.5in}

\item An chemical process used twenty-one thousand liters of water in seven hours. How many liters per hour did it use? 
  \vspace{0.5in}
  \vspace{0.5in}
  \vspace{0.5in}

\end{enumerate}
\end{document}
