\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - word problems \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. 

\begin{enumerate}
		\newcommand{\spacing}{\vspace{0.70in}}
\item Twelve pounds of material costs forty-eight dollars. How much is material per pound? 
\spacing

\item Material costs three dollars per pound. How much is twenty pounds? 
\spacing

\item If material costs \$5/lb., how much can you get for \$30? 
\spacing

\item It costs \$500 per hour to run the cell. How long can we run the cell for \$72,000? 
\spacing

\item It costs \$730 per hour to run the cell. How much will it cost to run the cell for sixty hours? 
\spacing

\item Running the cell for eight hours cost \$1,760. How much did it cost per hour? 
\spacing

\item Alice drove 350.8 miles on 19.6 gallons of gas. How many miles per gallon did Alice get, to the nearest unit? 
\spacing

\item If Zoe's car gets thirty-eight miles per gallon, how far can Zoe drive on sixteen gallons? 
\spacing

\item If the red car gets thirty-two miles per gallon, how many gallons does it need to go eight hundred miles? 
\spacing

\item The grinder removes $0.006$ inches per pass. How many passes does it take to remove $\dfrac{1}{32}$? Round up to the next whole number. 
\spacing

\item The grinder removes a total of $\dfrac{5}{32}$ of an inch in 8 passes. To the nearest thousandth of an inch, how much does it remove per pass? 
\spacing

\item To the nearest thousandth of an inch, how much material must be removed per pass in order to remove $0.05$ inches in eight passes? 
\spacing

\item The budget allows \$1,500 for fluid. 
	\begin{enumerate}
		\item A case of a dozen one-gallon cans costs \$275. How many cases can you get within budget, and how many gallons is that?  
\spacing

		\item A fifty-five-gallon drum costs \$700, plus \$80 for the necessary hand pump. How much is one hand pump and as many drums as you can get within budget, and how many gallons of fluid do you get? 
	\end{enumerate}

\end{enumerate}
\end{document}
