\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - percents - 4 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Unless directed otherwise, round answers to the nearest hundredth, or to the nearest percent. Show all of your work. You may use a calculator and notes. 
\begin{enumerate}
\newcommand{\spacing}{\vspace{0.70in}}
\item The price of material last year was \$72 per ton. Now it costs \$80 per ton. By what percent has the price increased? 
\spacing

\item Six months ago the price of a product was \$1,200. Since then the price has gone down by 25\%. What is the current price? 
\spacing

\item If gasoline decreased from \$3.00 per gallon to \$2.00 per gallon, by what percent did the price decrease? 
\spacing

\item If gasoline increased from \$2.00 per gallon to \$3.00 per gallon, by what percent did the price increase? 
  \vspace{0.50in}

\item If the production per shift decreased from 8,000 units to 7,500 units, by what percent did the production rate decrease? 
\spacing

\item From \$2,000 to \$2,800 is what percent increase? 
\spacing

\item A product that has been selling for \$38 is to be increased in price by 12\%. Find its new price. 
\spacing

\item An item regularly \$7.99 is on sale for 20\% off. What is its sale price? 
\spacing

\item The new structural element is to be 40\$ thicker than the old one. If the old one was 82 mm thick, how thick should the new one be, rounded to the nearest millimeter? 
\spacing

\item The basic item is 48 inches long. The deluxe item is 60 inches. 
	\begin{enumerate}
		\item By what percent is the deluxe item longer than the basic item? 
		\spacing
		\item By what percent is the basic item shorter than the deluxe item? 
		\spacing
	\end{enumerate}

\item The length of part A must be within 12\% of 280 mm. What is the minimum length of part A? 
\spacing

\item After a price reduction of 20\%, an injection molding feeder unit sells for \$18,000. What was the price before the reduction? 
\spacing

\end{enumerate}
\end{document}
