\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - decimals - 3 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. 

For 1 through 4, write each item as a decimal number. 
\begin{multicols}{2}
\begin{enumerate}

    \item \hspace{0.250in} $800+90+5$
  \vspace{0.25in}

    \item \hspace{0.250in} $10+2+\dfrac{3}{10}+\dfrac{4}{100}$
  \vspace{0.25in}

    \item \hspace{0.250in} $\dfrac{5}{10}+\dfrac{8}{100}+\dfrac{8}{1000}$
  \vspace{0.25in}

    \item \hspace{0.250in} two hundred fifty-one \& $48/100$ 
  \vspace{0.25in}

\end{enumerate}
\end{multicols}
For 5 through 8, write each item in expanded form. 
\begin{multicols}{2}
\begin{enumerate}
\setcounter{enumi}{4}

\item \hspace{0.25in} $34$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $5.73$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $305.032$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $110.01$ 
  \vspace{0.25in}
  
\end{enumerate}
\end{multicols}
  \vspace{0.25in}
\begin{enumerate}
\setcounter{enumi}{10}
		\newcommand{\spacing}{\vspace{0.60in}}
\item Write each item as a fraction in lowest terms 
\begin{multicols}{2}
\begin{enumerate}

\item \hspace{0.25in} $0.6$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $0.52$ 
  \vspace{0.25in}

\item \hspace{0.25in} $0.05$ 
  \vspace{0.25in}

\item \hspace{0.25in} $0.0012$ 
  \vspace{0.25in}

\end{enumerate}
\end{multicols}
  \vspace{0.25in}

\item Multiply $12.8$ by $15.25$. Round the result to the nearest tenth. 
\spacing

\item Write as a decimal the length three hundred forty-two ten thousandths of an inch. 
\spacing

\item Round to the nearest tenth the sum of $14.53$, $-9.6$, and $32.11$. 
\spacing

\item Round to the nearest tenth the ratio of $8.22$ feet to $4.5$ feet.  
\spacing

\item Find to the nearest hundredth $73.163$ divided by $1.61$.  
\spacing

\item Divide $428.46$ by $24.51$. Round the quotient to the nearest hundredth.   
\spacing

\item A forty-pound bag of material costs \$21.99. How much does it cost per pound, to the nearest cent? 
\spacing

\item If a commodity costs \$3.19 per ton, how much is 48.4 tons, to the nearest cent? 
\spacing

\item A journey of a thousand miles required \$77.50 for gas. With gas at $2.89$ per gallon, how many miles per gallon did  Pat's van get, to the nearest tenth? 
\spacing

\item A piping system drains $3$ gallons per hour. To the nearest hour, how long does it take to move $10,000$ gallons? 
\spacing

\item Stock $\frac{7}{8}$ inch in diameter is to be reduced to $0.862$ inches in diameter. To the nearest thousandth of an inch, how much material must be removed? 
\spacing

\item A tool removes three hundredths of an inch in twenty-two seconds. How long does it take to the nearest second to remove two tenths of an inch? 
\spacing

\end{enumerate}
\end{document}
