\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem set - percents - 2 \\[0.5in]
\end{center}
Name: \rule{4.5in}{0.005in} Date: \rule{1in}{0.005in} 
  \vspace{0.25in}

Round percents to the nearest tenth of a percent, and other results to the nearest tenth. For items 1 through 9, fill in the blanks to make each true. 

\begin{enumerate}
		\newcommand{\spacing}{\vspace{0.50in}}

\item 3\% of 48 is \rule{0.5in}{0.005in}.
  \spacing

\item \rule{0.5in}{0.005in}\% of 38 is 12.
  \spacing

\item Nine percent of \rule{1.5in}{0.005in} is eighteen.
  \spacing

\item \rule{0.5in}{0.005in} percent of 42 is 60.
  \spacing

\item 10\% of 360 is \rule{0.5in}{0.005in}.
  \spacing

\item 14 percent of \rule{0.5in}{0.005in} is 174.
  \spacing

\item 83\% of 779 is \rule{0.5in}{0.005in}.
  \spacing

\item \rule{0.5in}{0.005in}\% of 146 is 68.
  \spacing

\item \rule{0.5in}{0.005in} percent of 417 is 941.
  \spacing

\item Fifty pounds of peanuts mixed with thirty pounds of cashews makes a mix that is what percent cashews? 
  \spacing

\item A mix is made up of five pounds of peanuts, two pounds of cashews, and three pounds of raisins. What is the percent of each? 
  \spacing

\item How many pounds of peanuts must be mixed with twelve pounds of cashews so that the cashews will be twenty percent of the mix? 
  \spacing

\item The two components of a mix are in a ratio of 3:2. What per cent of the mix is each? 
  \spacing

\item If peanuts and cashews are mixed in a ratio of 7:4, what percent of the mix is peanuts? 
  \spacing

\item Fifty-two pounds of mix is 64\% peanuts and the rest cashews. How many pounds of cashews are in the mix? 
  \spacing

\item The three components of a mix are in a ratio of 9:4:2. What percent of the mix is each? 
  \spacing

\item A mix is 84\% peanuts, with the rest cashews. What is the ratio of peanuts to cashews?
  \spacing

\item A mix is 72\% peanuts, 12\% cashews, and the rest raisins. What is the ratio of peanuts to cashews to raisins?
  \spacing

\end{enumerate}
\end{document}
