\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Problem Set - Decimals 2 \\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. 

For problems 1 through 4, round each decimal as indicated. 
\begin{multicols}{2}
\begin{enumerate}

    \item \hspace{0.250in} $982.5$; hundred
  \vspace{0.25in}

    \item \hspace{0.250in} $0.0007$; thousandth
  \vspace{0.25in}

    \item \hspace{0.250in} $8.97$; tenth
  \vspace{0.25in}

    \item \hspace{0.250in} $3.4212$; hundredth
  \vspace{0.25in}

\end{enumerate}
\end{multicols}
For problems 5 through 10, write each item as a decimal rounded to the nearest ten thousandth.
\begin{multicols}{2}
\begin{enumerate}
\setcounter{enumi}{4}

\item \hspace{0.25in} $\frac{3}{9}$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $\frac{9}{32}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $1\frac{7}{64}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $\frac{5}{48}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $5\frac{6}{7}$ 
  \vspace{0.25in}

\item \hspace{0.25in} $\frac{52}{19}$ 
  \vspace{0.25in}
  
\end{enumerate}
\end{multicols}
  \vspace{0.25in}
\begin{enumerate}
\setcounter{enumi}{10}
		\newcommand{\spacing}{\vspace{0.60in}}
\item Write as a fraction in lowest terms 
\begin{multicols}{2}
\begin{enumerate}

\item \hspace{0.25in} $0.4$ 
  \vspace{0.25in}
  
\item \hspace{0.25in} $0.32$ 
  \vspace{0.25in}

\item \hspace{0.25in} $0.55$ 
  \vspace{0.25in}

\item \hspace{0.25in} $0.248$ 
  \vspace{0.25in}

\end{enumerate}
\end{multicols}
  \vspace{0.25in}

\item Multiply $0.8$ by $0.25$. 
\spacing

\item Write as a decimal the length one hundred fifty-three thousandths of an inch. 
\spacing

\item Round to the nearest tenth the product of $1.4$ and $9.6$. 
\spacing

\item Round to the nearest tenth the ratio of $5.4$ feet to $2.3$ feet.  
\spacing

\item Find to the nearest hundredth $33.19$ divided by $16$.  
\spacing

\item Find to the nearest tenth $121.24$ divided by $1.5$.  
\spacing

\item Gas costs $2.89$ per gallon, and Pat's van gets $18$ miles per gallon. To the nearest cent, how much does it cost to drive $48$ miles? 
\spacing

\item A pump moves $48$ liters per hour. To the nearest hour, how long does it take to move $1100$ liters? 
\spacing

\item A workpiece $\frac{5}{8}$ inch thick is to be reduced to $\frac{19}{32}$ thick in four passes of a grinder. To the nearest thousandth of an inch, what thickness of material must be removed in each pass? 
\spacing

\item A tool can remove a maximum of three hundredths of an inch on each pass. How many passes are required to remove $\frac{7}{64}$ of an inch? 
\spacing

\item Which is cheaper per pound, $52$ pounds for \$12.89, or $100$ pounds for \$24.99? 

\end{enumerate}
\end{document}
