\documentclass[12pt]{article}
\usepackage{amssymb,amsmath,latexsym,gensymb,mdwlist,tikz,multicol,enumitem}
\usepackage{pgf}

% Page length commands go here in the preamble
\setlength{\oddsidemargin}{0in} % Left margin of 1 in + 0 in = 1 in
\setlength{\textwidth}{6.5in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
\setlength{\topmargin}{-0.5in}  % Top margin of 2 in -1 in = 1 in
\setlength{\textheight}{9in}  % Lower margin of 11 in - 9 in - 1 in = 1 in

\setlength{\parindent}{0in} %Set the length of the paragraph indentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\pagestyle{empty} % controls page numbering
\begin{center}
          Review 4\\[0.5in]
\end{center}
Name: \rule{4in}{0.005in} Date: \rule{1.5in}{0.005in} 
  \vspace{0.25in}

Solve each problem. Show all of your work. You may use a calculator and notes. 

\begin{enumerate}
\newcommand{\spacing}{\vspace{0.75in}}

\item If 4 barrels of flour cost \$15, what will 12 barrels cost? 
\spacing

\item A certain amount of bamboo will feed the pandas for ninety days: if the number of pandas is doubled, long will the same amount of bamboo feed them? 
\spacing

\item A certain job can be done in ten days if you work at it for five hours each day. How many days would it require to do the same job if you work at it for eight hours a day? 
\spacing
 
\item If I walk 196 miles in 6 days, how far can I walk, at the same rate, in 18 days? 
\spacing

\item If 8 lb. of sugar cost \$1.28, how much is sugar per pound? 
\spacing

\item If 300 barrels of reagent cost \$22,100, what will 120 barrels cost? 
\spacing

\item If 120 sheep yield 380 pounds of wool, how many pounds will 360 sheep yield? 
\spacing

\item Use a proportion to find the value of four hundred tons of material at six dollars per ton.  
\spacing

\item If a dog can complete a journey in 9 days, walking 8 hours a day, how many days will it require if the dog walks 10 hours a day? 
\spacing

\item Six oxen ate 360 pounds of grass in a month. How much grass total will we need next month if we get four more oxen? 
\spacing

\item What will 26.25 bushels of wheat cost, if 3.5 bushels cost \$9.60? 
\spacing

\item If $\frac{1}{3}$ of an ounce costs \$0.90, what will $1\frac{1}{2}$oz. cost, to the nearest cent? 
\spacing

\item Making 1250 parts required forty gallons of solvent. How much solvent is required for 10,000 parts? 
\spacing

\item A tree 5 feet tall casts a shadow 7 feet long. What is the height of a tree that casts a shadow 84 feet long, at the same time of day? 
\spacing

\end{enumerate}
\end{document}

